Making all equalities equal

### 2021-12-18 paper.lagda.tex
code cleaner with private variable

@@

\begin{code}
module Martin-Löf {ℓ} {A : Set ℓ} where

  data _≡_ (x : A) : A → Set ℓ where
    refl : x ≡ x
\end{code}

@@

\begin{code}
module FunExt {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
  open Martin-Löf

@@

\begin{code}
module CubicalEquality {ℓ} {A : Set ℓ} where
  postulate
    PathP : (A : I → Set ℓ) → A i0 → A i1 → Set ℓ

@@

\begin{code}
module CubicalResults {ℓ ℓ'} {A : Set ℓ} {B : Set ℓ'} where
  open import Cubical.Core.Primitives

@@

module _ {a ℓ} {A : Set a} where
  ≣-Type = A → A → Set ℓ
  private
    ℓ₁ = ℓ-max a ℓ

@@

  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
    constructor eq
    field
      ≣-≡-≡ : let
        x≡y : Type ℓ₁
        x≡y = x ≡ y

@@

    ≡-≡-≣ : let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y
    ≡-≡-≣ = sym ≣-≡-≡

  module _ {_≣_ : ≣-Type} where
    sym-Equality : (≡-≡-≣ : {x y : A} → let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y)
      → IsEquality _≣_
    sym-Equality ≡-≡-≣ = eq (sym ≡-≡-≣)

  record Equality : Set (ℓ-suc (ℓ-max a ℓ)) where
    constructor eqC
    field
      _≣_ : ≣-Type
      ⦃ isEquality ⦄ : IsEquality _≣_

@@

\begin{code}
liftIso : ∀ {a b} {A : Type a} {B : Type b}
  → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
liftIso {a} f = iso fun inv
  (λ x i → rightInv x i) (λ x i → leftInv x i)
\end{code}

@@

\begin{code}
module FinalEquality {A : Set} where
  open MainResult A

  ≐≅≡ : ∀ {a b} → Iso (a ≐ b) (a ≡p b)
  ≐≅≡ = iso j i (ptoc ∘ ji) (ptoc ∘ ij)
\end{code}

@@

\begin{code}
  ≐≡≡ : ∀ {a b} → (a ≐ b) ≡c (a ≡p b)
  ≐≡≡ = let lifted = liftIso ≐≅≡  in isoToPath lifted
\end{code}

@@

        x≣₂y : Type ℓ₁
        x≣₂y = x ≡₂ y

        in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
      eqsEqual₂ = eqsEqual _≡₁_ _≡₂_

@@

      module _ {_≣_ : ≣-Type} where
        sym-Equality₂ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡ x≣y)
          → IsEquality₂ _≣_
        sym-Equality₂ ≡-≡-≣ = eq (sym ≡-≡-≣)

>>>>

Private variables are required, so it is not necessary to redefine them later as an implicit variable.

\begin{code}
open import Cubical.Core.Primitives using (Level; ℓ-max)

private variable
  ℓ ℓ′ : Level
  A : Set ℓ
\end{code}

@@

\begin{code}
module Martin-Löf {A : Set ℓ} where
  data _≡_ (x : A) : A → Set ℓ where
    refl : x ≡ x
\end{code}

@@

\begin{code}
module FunExt {A : Set ℓ} {B : Set ℓ′} where
  open Martin-Löf

@@

\begin{code}
module CubicalEquality {A : Set ℓ} where
  postulate
    PathP : (A : I → Set ℓ) → A i0 → A i1 → Set ℓ

@@

\begin{code}
module CubicalResults {A : Set ℓ} {B : Set ℓ′} where
  open import Cubical.Core.Primitives

@@

module _ {ℓ} {A : Set ℓ′} where
  ≣-Type = A → A → Set ℓ
  private
    ℓ₁ = ℓ-max ℓ′ ℓ

@@

  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc ℓ₁) where
    constructor eq
    field
      ≣-≡-≡ : let
        x≡y : Type ℓ₁
        x≡y = x ≡ y

@@

    ≡-≡-≣ : let
      x≡y : Type ℓ₁
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y
    ≡-≡-≣ = sym ≣-≡-≡

  module _ {_≣_ : ≣-Type} where
    sym-Equality : (≡-≡-≣ : {x y : A} → let
      x≡y : Type ℓ₁
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y)
      → IsEquality _≣_
    sym-Equality ≡-≡-≣ = eq (sym ≡-≡-≣)

  record Equality : Set (ℓ-suc ℓ₁) where
    constructor eqC
    field
      _≣_ : ≣-Type
      ⦃ isEquality ⦄ : IsEquality _≣_

@@

\begin{code}
liftIso : {A : Type ℓ} {B : Type ℓ′}
  → Iso {ℓ} {ℓ′} A B → Iso {ℓ-max ℓ ℓ′} {ℓ-max ℓ ℓ′} A B
liftIso f = iso fun inv
  (λ x i → rightInv x i) (λ x i → leftInv x i)
\end{code}

@@

\begin{code}
module FinalEquality {A : Set} where
  open MainResult A
  private variable
    x y z : A

  ≐≅≡ : Iso (x ≐ y) (x ≡p y)
  ≐≅≡ = iso j i (ptoc ∘ ji) (ptoc ∘ ij)
\end{code}

@@

\begin{code}
  ≐≡≡ : (x ≐ y) ≡c (x ≡p y)
  ≐≡≡ = let lifted = liftIso ≐≅≡  in isoToPath lifted
\end{code}

@@

        in x≣₁y ≡ (x ≡₂ y)
      eqsEqual₂ = eqsEqual _≡₁_ _≡₂_

@@

      module _ {_≣_ : ≣-Type} where
        sym-Equality₂ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          in x≡y ≡ (x ≣ y))
          → IsEquality₂ _≣_
        sym-Equality₂ ≡-≡-≣ = eq (sym ≡-≡-≣)
